A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games

### 2014-08-08 paper.tex
computing best response strategy using preconditioned primal-dual algorithm

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathbb{R}^{m, n}$ \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{p.c.l.s.c}: \quad acronym for \textit{proper convex lower semi-continuous};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{p.c.l.s.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{p.c.l.s.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

@@

Furthermore, one easily checks that $F^*$ and $G$ are \textit{p.c.l.s.c} with resolvent
(a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

>>>>

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

@@

Furthermore, one easily checks that $F^*$ and $G$ are \textit{l.s.c.p.c} with resolvent
(a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}
